Covid-19 A Spatio-Temporal Investigation.

### 2021-01-08 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 The main goal of this paper is to present methods used to identify spatial and spatio-temporal dependence in the number of infections and deaths caused by COVID-19, so they can be used in future or hypothetical situations where is necessary to investigate the behavior of a pathogen agent in space and time. The spatial method was calculated by using the Global Moran's I and the Local Moran's I $\!\!^4$, which is also known as a LISA statistic (Local Indicator of Spatial Association), both being used as indicators of spatial association. Spatio-temporal association was evaluated by computing a spatio-temporal Poisson scan statistic, proposed by Kulldorff (place reference here) to identify emerging or "alive" *clusters* in space and time.

@@

[5] - Guidotti, E., Ardia, D., (2020), “COVID-19 Data Hub”, Journal of Open Source Software 5(51):2376, doi: 10.21105/joss.02376.

@@

[10] - Kulldorff, M. (2001). Prospective time periodic geographical disease surveillance using a scan statistic. Journal of the Royal Statistical Society: Series A (Statistics in Society), 164(1), 61–72. doi:10.1111/1467-985x.00186

>>>>

 The main goal of this paper is to present methods used to identify spatial and spatio-temporal dependence in the number of infections and deaths caused by COVID-19, so they can be used in future or hypothetical situations where is necessary to investigate the behavior of a pathogen agent in space and time. The spatial method was calculated by using the Global Moran's I and the Local Moran's I $\!\!^4$, which is also known as a LISA statistic (Local Indicator of Spatial Association), both being used as indicators of spatial association. Spatio-temporal association was evaluated by computing a spatio-temporal Poisson scan statistic, proposed by Kulldorff $\!\!^5$ to identify emerging or "alive" *clusters* in space and time.

@@

[10] - Guidotti, E., Ardia, D., (2020), “COVID-19 Data Hub”, Journal of Open Source Software 5(51):2376, doi: 10.21105/joss.02376.

@@

[5] - Kulldorff, M. (2001). Prospective time periodic geographical disease surveillance using a scan statistic. Journal of the Royal Statistical Society: Series A (Statistics in Society), 164(1), 61–72. doi:10.1111/1467-985x.00186
